### 2020-01-30 wuhan.tex
tweaks

We evaluate six disparate models posted online between January 24--26, 2020 that estimated \Ro\ for the 2019-nCoV outbreak. We use our framework to construct pooled estimates for the underlying parameters. We use these pooled estimates to illustrate the importance of propagating different sources of error, particularly uncertainty in both the growth rate and the generation interval. We also use our framework to unravel which assumptions of these different models led to their different estimates and confidence intervals.

Our results indicate that many early estimates of \Ro\ were likely overly confident.

@@

We gathered information on estimates of $\mathcal R_0$ and their assumptions about the underlying generation-interval distributions from 6 articles that were uploaded to preprint servers between January 24th, 2020 and January 26th, 2020 (Table 1).
For each study $i$, we analyze explicitly or implicitly reported distributions of the reproductive number $\mathcal R_{0i}$, the mean generation interval $\bar G_i$, and the generation-interval dispersion parameter $\kappa_i$ (equivalent to the squared coefficient of variation for a gamma distribution, which matched the assumptions of all of the studies).
We modeled values reported using gamma distributions or confidence intervals with gamma distributions, and values reported using uniform distributions with uniform distributions \jd{SWP pls check}.
For example, Study 2 estimated $\mathcal R_0 = 2.92$ (95\% CI: 2.28--3.67);
we model this parameter as a gamma distribution with a mean of 2.92 and a shape parameter of 67, which has a 95\% probability of containing a value between 2.28 and 3.67 (see Table 2 for a complete description).
If a study assumed a fixed value for a parameter, we hold that parameters constant as well, using the same assumed value. \jd{I kind of want to drop this sentence.}

We then constructed a family of parameter sets for each study, and used these in a Bayesian multilevel model to build a distribution of pooled estimates (see Methods).

@@

We construct pooled estimates for each parameter ($r$, $\bar G$, and $\kappa$) using a Bayesian multilevel modeling approach, which assumes that the parameters across different studies come from the same Gamma distribution:
\begin{equation}
\begin{aligned}
r_i &\sim \mathrm{Gamma}(\mathrm{mean}=\mu_r, \mathrm{shape}=\alpha_r),\\
\bar{G}_i &\sim \mathrm{Gamma}(\mathrm{mean}=\mu_G, \mathrm{shape}=\alpha_G),\\
\kappa_i &\sim \mathrm{Gamma}(\mathrm{mean}=\mu_\kappa, \mathrm{shape}=\alpha_\kappa).\\
\end{aligned}
\end{equation}
We account for uncertainties associated with $r_i$, $\bar G_i$ and $\kappa_i$ (and their correlations), by drawing a random set from the family of parameter sets for each study at each Metropolis-Hastings step;
this approach is analogous to Bayesian methods for analyzing phylogenetic data, which often rely on drawing random samples of phylogenetic trees from a discrete set to account for phylogenetic uncertainty \citep{pagel2004bayesian,bedford2014integrating}.
Weakly informative priors are assumed on the hyperparameters:
\begin{equation}
\begin{aligned}
\mu_r &\sim \mathrm{Gamma}(\mathrm{mean}=0.1\,\mathrm{day}^{-1},\,\mathrm{shape}=0.1)\\
\mu_G &\sim \mathrm{Gamma}(\mathrm{mean}=1\,\mathrm{week},\,\mathrm{shape}=0.1)\\
(\mu_\kappa, \alpha_r, \alpha_G, \alpha_\kappa) &\sim \mathrm{Gamma}(\mathrm{mean}=1,\,\mathrm{shape}=0.1).
\end{aligned}
\end{equation}
We run 4 parallel Markov Chain Monte Carlo (MCMC) chains that consist of 200,000 burnin steps and 200,000 sampling steps.
Posterior samples are thinned every 400 steps.
Convergence is assessed by ensuring that the Gelman-Rubin statistic is below 1.01 for all parameters \citep{gelman1992inference}.

>>>>

We evaluate six disparate models posted online between January 24--26, 2020 that estimated \Ro\ for the 2019-nCoV outbreak. We use our framework to construct pooled estimates for the underlying parameters. We use these pooled estimates to illustrate the importance of propagating different sources of error, particularly uncertainty in both the growth rate and the generation interval. We also use our framework to unravel which assumptions of these different models led to their different estimates and confidence intervals.
Our results indicate that many early estimates of \Ro\ were likely overly confident.

@@

We gathered information on estimates of $\mathcal R_0$ and their assumptions about the underlying generation-interval distributions from 6 articles that were uploaded to preprint servers between January 24th, 2020 and January 26th, 2020 (Table 1).
For each study $i$, we analyze explicitly or implicitly reported distributions of the reproductive number $\mathcal R_{0i}$, the mean generation interval $\bar G_i$, and the generation-interval dispersion parameter $\kappa_i$ (equivalent to the squared coefficient of variation for a gamma distribution, which matched the assumptions of all of the studies).
We modeled values reported using confidence intervals with gamma distributions, and values reported using ranges with uniform distributions.
For example, Study 2 estimated $\mathcal R_0 = 2.92$ (95\% CI: 2.28--3.67);
we model this parameter as a gamma distribution with a mean of 2.92 and a shape parameter of 67, which has a 95\% probability of containing a value between 2.28 and 3.67 (see Table 2 for a complete description).
We then constructed a family of parameter sets for each study, and used these in a Bayesian multilevel model to build a distribution of pooled estimates (see Methods).

\begin{table}[t]
\begin{center}
\footnotesize
\begin{tabular}{l|l|l|l}
 & Basic reproductive number & mean generation time (days) & CV$^2$ generation time \\
\hline
Study 1 & $\mathrm{Gamma}(\alpha=28, \beta=28/2.6)$ & constant & constant \\
\hline
Study 2 & $\mathrm{Gamma}(\alpha=67, \beta=67/2.92)$ & constant & constant \\
\hline
Study 3 & N.A.$^\ast$ & $\mathrm{Uniform}(6, 10)$ & constant\\
\hline
Study 4 & $\mathrm{Gamma}(\alpha=1400, \beta=1400/3.8)$ & constant & constant \\
\hline
Study 5 & $\mathrm{Gamma}(\alpha=12, \beta=12/2.2)$ & $\mathrm{Uniform}(7, 14)$ & constant\\
\hline
Study 6 & $\mathrm{Gamma}(\alpha=54, \beta=54/5.47)$ & $\mathrm{Uniform}(7.6, 8.4)$ & constant
\end{tabular}
\end{center}
\caption{
\textbf{Probability distributions $\mathcal R_0$, $\bar G$, and $\kappa$.}
We use these 
The probability distribution for the exponential growth rate $r$ for each study is obtained by drawing random samples from these distributions and taking the inverse of \eref{gamma}.
The gamma distribution is parameterized by shape $\alpha$ and rate $\beta$ parameters.
Constant distributions assume a fixed values according to Table 1.
$^\ast$Study 3 effectively fits an exponential curve to the cumulative number of confirmed cases. \emph{All} uncertainty in their $\mathcal R_0$ estimate can be explained by the uncertainty range they consider for $\bar G$. Instead of modeling $\mathcal R_0$ with a probability distribution and recalculating $r$, we simply fix $r=0.114\,\mathrm{days}^{-1}$.
}
\end{table}

@@

We construct pooled estimates for each parameter ($r$, $\bar G$, and $\kappa$) using a Bayesian multilevel modeling approach, which assumes that the parameters across different studies come from the same Gamma distribution:
\begin{equation}
\begin{aligned}
r_i &\sim \mathrm{Gamma}(\mathrm{mean}=\mu_r, \mathrm{shape}=\alpha_r),\\
\bar{G}_i &\sim \mathrm{Gamma}(\mathrm{mean}=\mu_G, \mathrm{shape}=\alpha_G),\\
\kappa_i &\sim \mathrm{Gamma}(\mathrm{mean}=\mu_\kappa, \mathrm{shape}=\alpha_\kappa).\\
\end{aligned}
\end{equation}
We account for uncertainties associated with $r_i$, $\bar G_i$ and $\kappa_i$ (and their correlations), by drawing a random set from the family of parameter sets for each study at each Metropolis-Hastings step;
this approach is analogous to Bayesian methods for analyzing phylogenetic data, which often rely on drawing random samples of phylogenetic trees from a discrete set to account for phylogenetic uncertainty \citep{pagel2004bayesian,bedford2014integrating}.
Weakly informative priors are assumed on the hyperparameters:
\begin{equation}
\begin{aligned}
\mu_r &\sim \mathrm{Gamma}(\mathrm{mean}=1\,\mathrm{week}^{-1},\,\mathrm{shape}=0.1)\\
\mu_G &\sim \mathrm{Gamma}(\mathrm{mean}=1\,\mathrm{week},\,\mathrm{shape}=0.1)\\
(\mu_\kappa, \alpha_r, \alpha_G, \alpha_\kappa) &\sim \mathrm{Gamma}(\mathrm{mean}=1,\,\mathrm{shape}=0.1).
\end{aligned}
\end{equation}
We run 4 parallel Markov Chain Monte Carlo (MCMC) chains that consist of 200,000 burnin steps and 200,000 sampling steps.
Posterior samples are thinned every 400 steps.
Convergence is assessed by ensuring that the Gelman-Rubin statistic is below 1.01 for all parameters \citep{gelman1992inference}.
